Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-27 aistats.tex
Minimal change to incorporate the caveat

These functions are neither smooth, nor strongly convex, and $\conj$ is self-concordant
\citep[p.177, example 4.1.1.4]{nesterov2003introductory}
, but $\logpart$ is not (see App.~\ref{app:gaussian}).
We now discuss the general problem and some ways to solve it via direct expansions of the Bregman divergence.

@@

The entropy $\conj$ is self-concordant for several common families.
For instance Gaussians (\S\ref{ssec:gaussian}), or when $T$ is 1-dimensional and $\logpart$ is self-concordant (App.~\ref{app:self-concordant}),
as is the case with:
exponential distributions,
Laplace with known mean,
Pareto with known minimum value,
or Weibull with known shape $k$.
The entropy is also self-concordant when $T$ lives in a compact \citep{bubeck2015entropic} -- e.g., categorical and Dirichlet distributions.
Precisely, categorical variables illustrate that Proposition~\ref{prop:selfConcordant} does not imply directly a bound on the \emph{expected} Bregman.
The expected KL of the categorical MLE is always infinite, as previously mentioned in \S\ref{sec:problem}.

@@

More generally, these results answer~\eqref{problem} only \emph{partially} for the following reasons.
First, the present proposition and these related works all give \textit{large sample} results,  that hold when $n\geq N$ for some constant $N$. 
None of them apply to small $n$.
Second, they do not apply to some standard exponential families like the full Gaussian example that we saw in \S\ref{ssec:gaussian}  for which $f$ is \emph{not} self-concordant. 
A full solution to~\eqref{problem} would address these caveats.
Informed by the properties that we have seen so far, we next investigate a general decomposition of the Bregman that could guide us towards a solution.

@@

\addcontentsline{toc}{section}{Appendix} % Add the appendix text to the document TOC
\part{Appendix} % Start the appendix part
\begin{important}
	{\bf Erratum:} contrary to what is written in the main text in the last paragraph of Section~\ref{ssec:gaussian} and~\ref{ssec:local-quadratic}, the log-partition of a full Gaussian \emph{is} self-concordant. See \cref{app:gaussian} for details. This does not change the narrative of the paper though.
\end{important}
\parttoc % Insert the appendix TOC

@@

\begin{important}
	{\bf Erratum:}  
	In the main text, we claimed by mistake in the last paragraph of Section~\ref{ssec:gaussian} and~\ref{ssec:local-quadratic} that the log-partition of a full Gaussian is not self-concordant. 
	There was an error in our derivations and we will now prove the opposite (using classical results).
	However, this does not change our main story, and in particular, the point that we made in the last paragraph of Section~\ref{ssec:local-quadratic} that there is a lack of results in the few sample regime remains valid.
	%TODO ostroskii and bach are using a subgaussian assumption which does not hold for a Gaussian, so there might still be work to do. But also check anastasiou to be sure.
\end{important}

>>>>

These functions are neither smooth, nor strongly convex, but they are self-concordant, since $\conj$ is  the logarithmic barrier of a quadratic domain
\citep[p.177, example 4.1.1.4]{nesterov2003introductory}, and self-concordance is preserved by convex-conjugacy~\citep{nesterov1994interior} -- see more details in App.~\ref{app:gaussian}.
We now discuss the general problem and some ways to solve it via direct expansions of the Bregman divergence.

@@

The entropy $\conj$ is self-concordant for several common families such as Gaussians (\S\ref{ssec:gaussian}). %or gamma ?
Since self-concordance is preserved by convex-conjugacy~\citep{nesterov1994interior}, we can add to the list:
exponential distributions,
Laplace with known mean,
Pareto with known minimum value,
Weibull with known shape $k$.
The entropy is also self-concordant when $T$ lives in a compact \citep{bubeck2015entropic} -- e.g., categorical and Dirichlet distributions.
Precisely, categorical variables illustrate that Proposition~\ref{prop:selfConcordant} does not imply directly a bound on the \emph{expected} Bregman.
The expected KL of the categorical MLE is always infinite, as previously mentioned in \S\ref{sec:problem}.

@@

More generally, the present proposition and these related works answer~\eqref{problem} only \emph{partially}, as they all give \textit{large sample} results, that hold when $n\geq N$ for some constant $N$. 
A full solution to~\eqref{problem} would apply to small $n$.
Informed by the properties that we have seen so far, we next investigate a general decomposition of the Bregman that could guide us towards a solution.

@@

\addcontentsline{toc}{section}{Appendix} % Add the appendix text to the document TOC
\part{Appendix} % Start the appendix part
\parttoc % Insert the appendix TOC

@@

%TODO ostroskii and bach are using a subgaussian assumption which does not hold for a Gaussian, so there might still be work to do. But also check anastasiou to be sure.
